\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex
Added some conclusiony words

Figure \ref{fig:comp_3} compares translational and rotational root mean squared error (RMSE) of the MSCKF, SWF, and pure IMU integration on three synthetic datasets with 40, 60, and 100 features.
On all three datasets, the SWF outperforms the MSCKF by a wide margin, although the MSCKF's performance improves as more features are added.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS} \label{sec:conclusions}
Things quickly got out of hand when Matlab achieved sentience. 
We were forced to abandon our lab and have been surviving in the harsh environment of the MarsDome for weeks.
If this ever gets published, please send help!

>>>>

Figure \ref{fig:comp_3} compares translational and rotational root mean squared error (RMSE) of the MSCKF, SWF, and pure IMU integration on three synthetic datasets with 40, 60, and 100 features.
With additional features, both algorithms consistently outperform pure IMU integration, and the SWF outperforms the MSCKF by a wide margin on all three datasets.
Note that the MSCKF's performance improves as the number of features increases while the SWF's performance is not significantly affected by increasing feature count.
This result indicates that the MSCKF is much more sensitive to feature density than the SWF.

@@

Table [TABLETABLETABLE] provides summary statistics of each algorithm's performance on the synthetic datasets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS} \label{sec:conclusions}
Based on our experimental results, we conclude that neither the SWF nor the MSCKF is more effective than pure IMU integration in environments with few features.
In environments with more features, both algorithms provide substantial gains over pure IMU integration, although the SWF significantly outperformed the MSCKF on the datasets we tested.
However, the accuracy of the MSCKF improves as more features are added, while the SWF is less sensitive to feature quantity.
It is unclear from these results which algorithm would perform best in the limit of infinite features.

[Something something consistency NEES]

It is worth noting that although the SWF achieved superior accuracy in most cases, the computational effort it required was significantly greater than for the MSCKF.
The MSCKF may therefore be better suited to vehicles with limited computational resources, particularly if they are operating in feature-rich environments.
